Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-20 VMCAI-revised-version/final.tex
transmission des modifications sur l'abstract

	\noindent	
	where TM$_j$ is the $j$-th Turing machine (in a classical enumeration)
	which moreover begins
by writing the integer $j$ on its tape,	
	and consider additionnally the function $g : \N^2 \to \N^2$ defined by $g(n,k) = (n+1,k)$. 
	The
	transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ 
	is a $\post$-effective $\omega^2$-WSTS with strong compatibility
	and
	has the property that
	it is
	$\mathop{\uparrow} (1,1)$-resilient
	iff TM$_j$ halts on input $j$,
	since $(1,1)$ is coverable from $(0,0)$
	iff TM$_j$ halts on input $j$. 
	Hence there is no Turing machine which correctly determines 
	resilience and halts whenever its input is a
	WSTS.
Hence resilience for $\omega^2$-WSTS with strong compatibility is undecidable.\qed
\end{proof}
 Let us remark that the transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ in the previous proof is not $\post$-ideal-effective.

\mathieu{Reviewer 1: the example at the bottom of page 8, even if it is a WSTS, is a very particular case [...] wonder if classes containing such  systems are interesting per se. }

@@

\begin{proof}
The resilience problem can be reformulated as 
$\Bad \subseteq  \pred^*(\Safe)$ that is equivalent to $\Bad \cap (S \setminus \pred^*(\Safe)) = \emptyset$.
The set $\pred^*(\Safe)$ is upward-closed, since $\Safe$ is upward-closed. Since $\mathscr{S}=(S,\rightarrow, \leq)$ is $\pred$-basis-effective, we can compute a basis of $\pred^*(\Safe)$.
Since the wqo is ideally-effective, we can compute the intersection of
$\Bad$
and
$S \setminus \pred^*(\Safe)$,
which are both downward-closed, and test if this intersection is empty or not. Hence, the resilience problem is decidable. \qed\end{proof} 
%%%%%%%
\alain{prouver, si possible, les deux autres résilience}

@@

In the case of (upward compatible) WSTS with $\pred$-basis-effectivity, {\sc Resilience} is undecidable.

>>>>

	\noindent	
	where TM$_j$ is the $j$-th Turing machine (in a classical enumeration)
	which moreover begins
by writing the integer $j$ on its tape,	
	and consider additionnally the function $g : \N^2 \to \N^2$ defined by $g(n,k) = (n+1,k)$. 
	The
	transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ 
	is a $\post$-effective $\omega^2$-WSTS with strong compatibility
	and
	has the property that
	it is
	$\mathop{\uparrow} (1,1)$-resilient
	iff TM$_j$ halts on input $j$,
	since $(1,1)$ is coverable from $(0,0)$
	iff TM$_j$ halts on input $j$. 
	Hence there is no Turing machine which correctly determines 
	resilience and halts whenever its input is a
	WSTS.
Hence resilience for $\omega^2$-WSTS with strong compatibility is undecidable.\qed
\end{proof}
 Let us remark that the transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ in the previous proof is not $\post$-ideal-effective
	nor $\pred$-effective.

\mathieu{Reviewer 1: the example at the bottom of \textbf{ page 8} (now 10), even if it is a WSTS, is a very particular case [...] wonder if classes containing such  systems are interesting per se. }

In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable.

@@

\begin{proof}
The resilience problem can be reformulated as 
$\Bad \subseteq  \pred^*(\Safe)$ that is equivalent to $\Bad \cap (S \setminus \pred^*(\Safe)) = \emptyset$.
The set $\pred^*(\Safe)$ is upward-closed, since $\Safe$ is upward-closed. Since $\mathscr{S}=(S,\rightarrow, \leq)$ is $\pred$-basis-effective, we can compute a basis of $\pred^*(\Safe)$.
Since the wqo is ideally-effective, we can compute the intersection of
$\Bad$
and
$S \setminus \pred^*(\Safe)$,
which are both downward-closed, and test if this intersection is empty or not. Hence, the resilience problem is decidable. \qed\end{proof} 
%%%%%%%
%%\alain{prouver, si possible, les deux autres résilience}
Strong compatibility implies furthermore the decidability
of {\sc $k$-resilience} and {\sc bounded-resilience}.

@@
